### 2019-06-25 methodology/novel-contributions.tex
updates novel contributions

\section{Novel contributions}\label{sec:novel-contributions}
 \todo{tengo qui o sposto nel cap 4?}
 \subsection{Motivation} 
 The inspiration for the work carried out in this thesis was the paper \enquote{Explaining the Most Probable Explanation} by \cite{Butz2018}, that has been presented in detail in Sec. \ref{sec:explaining-mpe}.
 This paper proposed a system that would build a Bayesian Network to model a medical data set and, through the interaction with a medical expert, distill an explanation tree.
 This tree, deemed to represent the solution to the MPE query, could then be used to generate a natural language explanation that the authors claim would lead to the extraction of extra knowledge from the original data set.

@@

 For these reason, I believe that building a proof-of-concept system whose logic was inspired by the method presented in the aforementioned paper and validating it with real medical experts would be an important step forwards in the direction of answering the following questions:
 Can the method of the paper be corroborated?
 Are Bayesian Networks a good ML model to bootstrap an explanation from?
 How good an explanation does the proposed method give, as validated by a domain expert?
 What improvements are there to be made?

 \todo{migliorare dopo aver fatto literature review perche avro piu idee}
\subsection{Theory}

\subsection{Algorithms}
\subsubsection{\enquote{Pseudo-MPE}}
\subsubsection{Alternative explanation branches}
\subsubsection{\enquote{Pseudo-MPE} from random evidence}

>>>>

\section{Novel contributions}\label{sec:novel-contributions}
 \todo{tengo qui o sposto nel cap 4?}
 \subsection{Motivation} 
 The inspiration for the work carried out in this thesis was the paper \enquote{Explaining the Most Probable Explanation} by \cite{Butz2018}, that has been presented in detail in Sec. \ref{sec:explaining-mpe}.
 This paper proposed a system that would build a Bayesian Network modelling a medical data set and, through the interaction with a medical expert, distill an explanation tree.
 This tree, deemed to represent the solution to the MPE query, could then be used to generate a natural language explanation that the authors claim would lead to the extraction of extra knowledge from the original data set.

@@

 For these reason, I believe that building a proof-of-concept system whose logic was inspired by the method presented in the aforementioned paper and validating it with real medical experts would be an important step forwards in the direction of answering the following questions:
 Can the method of the paper be corroborated?
 Are Bayesian Networks a good ML model to bootstrap an explanation from?
 How good an explanation does the proposed method give, as validated by a domain expert?
 What improvements are there to be made?
 \todo{migliorare dopo aver fatto literature review perche avro piu idee}

\subsection{Theory}

\subsection{Algorithms}
An important part of my work was developing the algorithms needed to adapt the ideas presented in the paper \enquote{Explaining the Most Probable Explanation} by \cite{Butz2018} and \enquote{A Progressive Explanation of Inference in ‘Hybrid’ Bayesian} by \cite{Kyrimi2016}.
From the former, the construction of the probability tree through a constructive dialogue with the domain expert, the building of counterfactual explanation branches, the automatic generation of the most probable probability tree from initial evidence.
From the latter, the generation of an \enquote{Inverse explanation}.
Finally, an procedure to output a natural language explanation.

\subsubsection{\enquote{Pseudo-MPE}}
\todo{dove critico il fatto che non calcolano veramente l'MPE come dicevano? qui o in cap.4?}

\subsubsection{Alternative explanation branches}

\subsubsection{\enquote{Pseudo-MPE} from random evidence}

\subsubsection{Inverse explanation}
\todo{da fare e trovare nome migliore}

\subsubsection{Natural language explanation}
\todo{magari pensare anche a visual explanations?}
